Particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2025-11-17 AvdMomZvolA_examples/ips_examples.tex
UDC and MSC
[AMZA] Remove TODOs
[AMZA] Remove unnecessary theorem styles
[AMZA] Memorial note

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\theoremstyle{dfn}
\newtheorem{dfn}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

@@

@@

@@

How do we describe an integral point set?
For example, by the number of points in it, which is always finite~\cite{anning1945integral,erdos1945integral}
and is said to be the \emph{cardinality} of the IPS.
Furthermore, we can naturally % TODO: naturally/essentially? cf. arxiv/1
define the diameter of a finite point set.

@@

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
although the set is of characteristic 1,
it cannot be extended by the reflection in the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.
%
%TODO: write about points which prevent the set from reflection
%
\begin{equation}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	%\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{equation}
%
\begin{figure}[h!]
\center{\includegraphics[width=0.6\linewidth]{./img/8_2535_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

@@

>>>>

\theoremstyle{dfn}
\newtheorem{dfn}{Definition}

@@

To the blessed memory of Professor Semën Samsonovich Kutateladze
% Я взял такое написание с
% https://mathscinet.ams.org/mathscinet/MRAuthorID/197072
% и никоим образом на нём не настаиваю

@@

UDC 519.146 + 514.11

MSC 52C10

@@

How do we describe an integral point set?
For example, by the number of points in it, which is always finite~\cite{anning1945integral,erdos1945integral}
and is said to be the \emph{cardinality} of the IPS.
Furthermore, we can naturally
define the diameter of a finite point set.

@@

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
although the set is of characteristic 1,
it cannot be extended by the reflection in the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.

\begin{equation}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	%\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{equation}
%
\begin{figure}[h!]
\center{\includegraphics[width=0.6\linewidth]{./img/8_2535_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

@@

Special remark from N. Avdeev:
I would like to express my deepest gratitude to the late Professor Semën Samsonovich Kutateladze,
who played a pivotal role in my scientific career.
He recommended the journal for my first significant scholarly article~\cite{our-mz-rus-translit}
and facilitated its submission, marking the start of a pioneering series of works on this topic at our university.
This contribution is dedicated to his memory.
